High geomagnetic field intensity in the late Mesoproterozoic recorded by Midcontinent Rift anorthosite xenoliths

### 2021-08-28 manuscript/Manuscript.tex
Updates from Overleaf

\begin{keypoints}
\item new ca. 1092 Ma Midcontinent Rift anorthosite record high paleointensity values
\item high VADM of the geomagnetic field during the late Mesoproterozoic is inconsistent with previous interpretation of long term decay
\item a strong geodynamo like today likely persisted throughout 25 myr during the Midcontinent Rift development
\end{keypoints}

A few days into the new year of 2020, I arrived at Twin Cities, Minnesota for the first time, with an exciting rock magnetic project to be conducted at the Institute for Rock Magnetism. My research was focused on developing paleomagnetic data from the 1.1 Ga Beaver River diabase and its anorthosite xenoliths of the Beaver Bay Complex in North Shore, Minnesota. Before this trip, I had been developing directional and intensity data at the paleomagnetism lab at UC Berkeley. With the help of rock magnetic experiments at the IRM, I was hoping to decipher the cause of a variety of paleointensity results of my samples.

Retrieving paleomagnetic information from Precambrian rocks can aid in our understanding of the long-term evolution of the geodynamo. A recent paleointensity study by \cite{Sprain2018a} reported a ca. 1.1 Ga paleomagnetic field strength similar to today based on the volcanics of the Midcontinent Rift System (MRS). That study suggested that this result is consistent with models wherein this time period of the Proterozoic is characterized by a strong rather than weak geomagnetic field. However, to further evaluating the evolution of the geomagnetic field during the Precambrian, more paleointensity data are needed.

@@

\begin{abstract}

\end{abstract}

\section*{Plain Language Summary}
[ enter your Plain Language Summary here or delete this section]

\section{Introduction}

\section{Method}

\section{Results}

\section{Discussion}

\section{Conclusion}

>>>>

\begin{keypoints}
\item New ca. 1092 Ma Midcontinent Rift anorthosite record high paleointensity values
\item High VADM of the geomagnetic field during the late Mesoproterozoic is inconsistent with previous interpretation of long term decay
\item A strong geodynamo like today likely persisted throughout 25 myr during the Midcontinent Rift development
\end{keypoints}

% keywords: absolute paleointensity, Laurentia, Midcontinent Rift, anorthosite,

\begin{abstract}
High-quality absolute paleointensity

\end{abstract}
Retrieving paleomagnetic information from Precambrian rocks can aid in our understanding of the long-term evolution of the geodynamo. A recent paleointensity study by \cite{Sprain2018a} reported a ca. 1.1 Ga paleomagnetic field strength similar to today based on the volcanics of the Midcontinent Rift System (MRS). That study suggested that this result is consistent with models wherein this time period of the Proterozoic is characterized by a strong rather than weak geomagnetic field. However, to further evaluating the evolution of the geomagnetic field during the Precambrian, more paleointensity data are needed.

@@

\section*{Introduction}

\section*{Method}

\section*{Results}

\section*{Discussion}

\section*{Conclusion}
